14th International Satisfiability Modulo Theories Competition (SMT-COMP 2019): Rules and Procedures

### 2020-04-01 rules/rules20.tex
adding disclosure

  \item {\bf Limit the Number of Solvers.}
    This year solver development teams may only submit more than one
    entry if they are substantially different.  A justification must
    be provided for the difference.  We strongly encourage the teams
    to keep the number of solvers per team per category at at most
    two.
%
    \rationale{The organizers wishes to keep the total run-time of the
      competition small, in case of unforeseen problems that require
      to rerun the whole competition.  The idea in allowing up to two
      submissions is to encourage the development of new, experimental
      techniques by allowing an ``alternative solver'' to be submitted
      while keeping the competition manageable.}

@@

\header{Disclosure.}
%
\todo{add disclosure}
Jochen Hoenicke is part of the developing teams of the SMT solver
SMTInterpol~\cite{smtinterpol}.
Antti Hyvarinen is part of the developing team of the SMT solver
OpenSMT~\cite{opensmt2}.

>>>>

  \item {\bf Limit the Number of Solvers.}
    This year solver development teams may only submit more than one
    entry if they are substantially different.  A justification must
    be provided for the difference.  We strongly encourage the teams
    to keep the number of solvers per team per category at at most
    two.

    \rationale{The organizers wish to keep the total run-time of the
      competition small, in case of unforeseen problems that require
      to rerun the whole competition.  The idea in allowing up to two
      submissions is to encourage the development of new, experimental
      techniques by allowing an ``alternative solver'' to be submitted
      while keeping the competition manageable.}

@@

\header{Disclosure.}
%
Haniel Barbosa is part of the developing teams of the SMT solvers
CVC4~\cite{cvc4-smtcomp18} and veriT~\cite{verit}.
%
Jochen Hoenicke is part of the developing team of the SMT solver
SMTInterpol~\cite{smtinterpol}.
Antti Hyvarinen is part of the developing team of the SMT solver
OpenSMT~\cite{opensmt2}.
